%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://spotify.com}{ Spotify USA}} % Organization
    {New York, U.S.A} % Location
    {Mar. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement software tools and frameworks that support Spotify’s data processing and machine learning infrastructure.}
        \item {Architect and drive improvements on scalability, reliability, efficiency, and cost-effectiveness of Spotify’s data platform.}
        \item {Research, benchmark, assess and provide recommendations and guidelines on adoption and/or deprecation of data processing solutions that align with the data platform vision.}
        \item {Contribute to and maintain several open source software projects.}
        \item {Technology stack: GCP (GKE, BigQuery, BigTable, PubSub, Dataflow, Dataproc), Apache Flink, Trino, Kubernetes, Flyte, Scala, Java, C*, Elasticsearch, Python.}
      \end{cvitems}
    }

% ---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://spotify.com}{ Spotify USA}} % Organization
    {New York, U.S.A} % Location
    {Fev. 2018 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architect and lead the implementation of Spotify next gen data platform based on Apache Flink as execution engine.}
        \item {Scala ecosystem steward at Spotify.}
        \item {Implementation of tools and frameworks that compose the current Spotify data processing and machine learning infrastructure landscape.}
        \item {Mantainer of several open-source projects at Spotify; Scio, Featran, Zoltar, flink-on-k8s-operator, flyte-flink-plugin, etc.}
        \item {Technology stack: GCP (BigQuery, BigTable, PubSub, Dataflow, Dataproc, GKE), Apache Flink, Kubernetes, Flyte, Scala, Java, C*, Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://spotify.com}{Spotify, AB}} % Organization
    {Stockholm, Sweden} % Location
    {Sep. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented and maintained backend services, data and recommendation pipelines for the running \& party features.}
        \item {Reimplemented the main internal search API backend services.}
        \item {Optimized and Tunned the Elasticsearch clusters.}
        \item {Implemented a realtime content indexing pipeline.}
        \item {Technology stack: GCP (BigQuery, BigTable, PubSub, Dataflow, Dataproc), Scio, Apache Crunch, Scala, Java, C*, Elasticsearch, Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://outplay.com}{Outplay Entertainment}} % Organization
    {Dundee, Scotland} % Location
    {Mar. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead backend engineer.}
        \item {Developed highly available, scalable backends services like Leaderboard, Matchmaking, Notifications.}
        \item {Responsible for designing, planing and manage the entire infrastructure.}
        \item {Defined working processes in the team in order to achieve better collaboration.}
        \item {Implemented Continuous Integration environment.}
        \item {Technology stack: AWS (SNS, DynamoDB, EBS, ELB, EC2), Scala, Nginx, Go, Node.js, MongoDB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.doubletwist.com}{doubleTwist}} % Organization
    {San Francisco, U.S.A} % Location
    {Sep. 2012 - Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead backend engineer.}
        \item {Implemented all the backend infrastructure to support most of the client features. Account management, Payments, Podcasts and Radio streaming.}
        \item {Added a monitoring \& logging infrastructure.}
        \item {Implemented continuous integration environment.}
        \item {Technology stack: AWS(ELB , EBS, RDS, DynamoDB, SNS, EC2), Nginx, Scala, Python, Go}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Software Engineer} % Job title
    {\href{http://betabranch.com}{BetaBranch}} % Organization
    {Braga, Portugal} % Location
    {Jan. 2013 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consulting company, where we developed scalable and fault tolerant services for several companies.}
        \item {Developed a service for house tax evaluation. \url{http://imisimples.com}}
        \item {Technology stack: Scala, Haskell, Python, Django, Ruby on Rails, PostgreSQL, JavaScript}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://multicert.com}{Multicert, S.A}} % Organization
    {Porto, Portugal} % Location
    {Sep. 2010 - Sep. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developement of a Trust-service Status List management and issuing tool.}
        \item {Committer at CESeCore (http://cesecore.eu) a common security function Java library, provides a reusable base for implementing third-party trustworthy systems.}
        \item {Technology stack: Scala, Java, EJB, Glassfish, JBoss}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ALERT, Life Sciences Computing} % Organization
    {Porto, Portugal} % Location
    {Jan. 2008 - Spe. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of disaster recovery systems.}
        \item {Developed tools to improve deployment, decrease time and update risk.}
        \item {Developed tools to monitor and eval data quality in decision support systems.}
        \item {Evaluation of scalability and fault tolerant patterns.}
        \item {Technology stack: Java, Python, Oracle ODI, MicroStrategy, ORACLE DB, Tomcat}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
